---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)

```



# rasterwise

The goal of rasterwise is to collate hard-won knowledge of what's wrong and what's right about various data sets. 
It began as a collection of iillustrative NetCDF files, used for testing so our R code works right. 

## raadtools - a code collection of raster wise-dom

TBD

A classic example is old ocean surface data (Aviso) that was in a regular Mercator grid, but published with 
rectlinear lon-lat arrays

https://github.com/AustralianAntarcticDivision/raadtools/blob/master/R/fronts.R#L129-L142

There are many others https://twitter.com/mdsumner/status/1057504207043997697

## Contributing

Raise issues, send PRs, tell us your war stories! 

## Rogue NetCDF files


Files are put into "extdata/", and then a script is run to 

* archive all the files in extdata/ as a tarball
* generate a record of the list of files
* commit to the repo and tag the release
* push the tarball artefact out into the Releases files (using R's piggyback)

## Get the files

To download the entire file bundle run this code: 

```R
library(piggyback)
pb_download("weird.tar.gz", dest = ".", repo = "mdsumner/rasterwise", tag = "v0.5.0")
```

I often put the stars issue number into the folder name https://github.com/r-spatial/stars/issues

There are some weird and wonderful files in the extdata/ on their own, from my personal collections. 


## The list

```{r, echo=FALSE}
files <- readLines("weirdlist.txt")
writeLines(files)
```


## The ncdumps -h 


```{r,echo=FALSE}
for (i in seq_along(files)) {
  cat("###############################################################################\n")
  cat(files[i])
  cat("\n\n\n\n")
  dump <- system(sprintf("ncdump -h %s", file.path("extdata", files[i])), intern = TRUE)
  writeLines(dump)
  cat("\n\n\n\n")
}
```
